A graph-based data model for interactive evolutionary computation

### 2017-01-19 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
New bib files
Making some small corrections and changes
It's more important that @mariosky addresses some concerns in the
paper.

\begin{itemize}
  \item { \tt Individual-Individual} The relationships between individuals in the
  population are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be of interest
  for instance similarity or composition.

  \item {\tt User-Individual}
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection [cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals [cite ES-I].

  \item {\tt User-User}
  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user\'s preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users\' preferences.

@@

 % Can it be quantified? Maybe a reference to NodIO? - JJ
%Some authors have already tried to address this basic problem
%\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj
%% Moving this to Related Work Section -Mario

% Maybe this claim should go to the beginning. THIS is why we want to
% use them - JJ
% Done - Mario

@@

\begin{figure*}
\captionsetup{justification=centering,margin=2cm}
\centering
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.7pt}
\fbox{\includegraphics[width=12cm,height=10cm,keepaspectratio]{img/UI_ed01.png}}
\caption{User interface of an EvoSpace-Interactive application.}
\label{fig:web}       
\end{figure*}

@@

\subsection{Fitness Assignment}
\label{sec:col}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, data about individuals %what? Maybe data
                                %about individuals? - JJ
must be permanently stored, even
if they are no longer in the active population.

@@

At the top left corner list of Facebook friends is presented, 
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population 
is shown to the user.
Here, the user can interact with the system in two ways.
He can assign a quality assessment to the individual using
a five star rating measure.
Additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special directory to store individuals a user prefers and wishes
to save. After the user finishes interacting the individual
on the Wall, he can choose to retrieve a new one from population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

@@

\begin{figure*}
  \captionsetup{justification=centering,margin=2cm}
  \centering
  \setlength\fboxsep{0pt}
  \setlength\fboxrule{0.7pt}
  \fbox{\includegraphics[width=10cm,height=10cm,keepaspectratio]{img/framework.png}}
  \caption{User-Centerd Framework.}
  \label{fig:uc_framework}       
\end{figure*}

The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{evospace-i}
%\bibliography{languages}
\end{document}

>>>>

\begin{itemize}
  \item {\bf Individual-Individual} The relationships between individuals in the
  population are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be of interest
  for instance similarity or composition.

  \item {\bf User-Individual}
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection [cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals [cite ES-I].

  \item {\bf User-User}
  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user\'s preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users\' preferences.

@@

 % Can it be quantified? Maybe a reference to NodIO? - JJ
%Some authors have already tried to address this basic problem
%\cite{Frade:2010:EvoGAMES}. %Non sequitur. Is it something we are
                            %going to do here? - jj
%% Moving this to Related Work Section -Mario
% That section is not there yet. Forgot to paste? - JJ

@@

\begin{figure*}[h!tbp]
\captionsetup{justification=centering,margin=2cm}
\centering
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.7pt}
\fbox{\includegraphics[width=12cm,height=10cm,keepaspectratio]{img/UI_ed01.png}}
\caption{User interface of an EvoSpace-Interactive application.}
\label{fig:web}       
\end{figure*}

@@

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, data about individuals %what? Maybe data
                                %about individuals? - JJ
must be permanently stored, even
if they are no longer in the active population.

@@

At the top left corner a list of Facebook friends is presented
to encourage users to interact with the system. In the central 
\emph{ Wall } area, an individual sampled from the population that is
being evolved via the evolutionary algorithm 
is shown to the user.
Here, the user can interact with the system in two ways.
He can assign a quality assessment to the individual using
a five star rating measure.
Additionally, a user can choose to add an image to one of their \emph{Collections}.
A collection is a special directory to store individuals a user prefers and wishes
to save. After the user finishes interacting the individual
on the Wall, he can choose to retrieve a new one from population.
At the left side, is the \emph{Collections} section.
The user can create several collections, to group and organize his favorite 
artifacts. Moreover, a user can browse the content of each collection and from
there share images through the social network.
When a user browses over an individual a detail pane shows how many users have
liked the individual. The pane also includes a link to the individual's 
details, the parents, genetic operators that created it, and genealogy information.

@@

\begin{figure*}[h!tbp]
  \captionsetup{justification=centering,margin=2cm}
  \centering
  \setlength\fboxsep{0pt}
  \setlength\fboxrule{0.7pt}
  \fbox{\includegraphics[width=10cm,height=10cm,keepaspectratio]{img/framework.png}}
  \caption{User-Centered Framework.} %Maybe a bit of more explanation,
                                %showing the relationships and what
                                %they mean.
  \label{fig:uc_framework}       
\end{figure*}
%
The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{evospace-i,volunteer}
%\bibliography{languages}
\end{document}
